Append_smoothed_results

### 2016-12-16 Code/append_smoothed_results.Rmd
LE for overall US

>>>>

```{r calculate_overall_LE}
dat.smoothed.aggregatedCOD$YearRaceSex <- interaction(dat.smoothed.aggregatedCOD$Year3, dat.smoothed.aggregatedCOD$Race2, 
                                                      dat.smoothed.aggregatedCOD$Sex2)

dat.smoothed.US <- dat.smoothed.aggregatedCOD %>% 
  ungroup() %>% group_by(Year2, RaceSex, Age2) %>%
  arrange(YearRaceSex, Age2) %>%
  summarise(US_smoothed_deaths = sum(total_smoothed_deaths),
            US_population = sum(Population), 
            nx = first(nx),
            Age3 = first(Age3),
            Year3 = first(Year3),
            YearRaceSex = first(YearRaceSex),
            Sex2 = first(Sex2),
            Race2 = first(Race2))

US.stratum.id <- unique(dat.smoothed.US$YearRaceSex)

US.life.tables <- vector(mode = "list", length = length(US.stratum.id))
list.index <- 1

#runs in a few seconds
for (stratum.i in US.stratum.id) {

  US.life.tables[[list.index]] <- life.table(data = subset(dat.smoothed.US, YearRaceSex == stratum.i), 
                                    num.ages.in.group = "nx", 
                                    death.counts = "US_smoothed_deaths", 
                                    population.counts = "US_population")
  list.index <- list.index + 1
}
```
